%-------------------------
% Resume in Latex
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor} % 建議統一使用 xcolor 並帶入顏色參數
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% 分頁與標題樣式設定
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% 修正 Unicode 設定
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
\textbf{#1} & #2 \\
\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% 重要：將 pagecolor 放在這裡，解決編譯錯誤與黑底問題
\pagecolor{white}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Chung-Chin Huang} \\ \vspace{4pt}
    +886-984-301-459 $|$ 
    \href{mailto:99godgod@gmail.com}{\underline{99godgod@gmail.com}} $|$ 
    \href{https://github.com/dogdog99}{\underline{github.com/dogdog99}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National Cheng Kung University}{Tainan, Taiwan}
      {M.S. in Applied Mathematics}{2025 -- Present}
      \resumeItemListStart
        \resumeItem{Specializing in \textbf{Scientific Computing} and \textbf{Numerical Methods for PDEs}.}
        \resumeItem{Researching computational mathematics, including \textbf{Finite Difference (FDM)} and \textbf{Finite Element Methods (FEM)}.}
      \resumeItemListEnd

    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Hsinchu, Taiwan}
      {Studies in Mathematics}{2022 -- 2025}
      \resumeItemListStart
        \resumeItem{Advanced coursework in Mathematical Analysis, Probability Theory, and Linear Algebra.}
      \resumeItemListEnd

    \resumeSubheading
      {National Taiwan University}{Taipei, Taiwan}
      {B.S. in Environmental Engineering}{2019 -- 2021}
      \resumeItemListStart
        \resumeItem{Foundational CS coursework: Data Structures, Algorithms, and Operating Systems.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {National Yang Ming Chiao Tung University}{Mar 2024 -- Nov 2024}
      {Web Developer / Administrative Assistant}{Hsinchu, Taiwan}
      \resumeItemListStart
        \resumeItem{Developed and optimized the front-end architecture for the Liberal Arts College website.}
        \resumeItem{Ensured compliance with \textbf{ISO/IEC 27001} standards for information security management (ISMS).}
        \resumeItem{Maintained system stability and performed regular security audits and updates.}
      \resumeItemListEnd

    \resumeSubheading
      {System Developer}{Sep 2021 -- Feb 2024}
      {Independent Project (Linux/C)}{}
      \resumeItemListStart
        \resumeItem{Designed and deployed a high-performance cryptocurrency mining system on \textbf{Linux} servers.}
        \resumeItem{Developed custom automation scripts in \textbf{C} for hardware monitoring and workload optimization.}
        \resumeItem{Managed network configuration and performed real-time debugging for distributed systems.}
      \resumeItemListEnd

    \resumeSubheading
      {EYESCREAM / Yiqi International Co., Ltd.}{Jul 2019 -- Feb 2020}
      {IT Assistant}{Taipei, Taiwan}
      \resumeItemListStart
        \resumeItem{Maintained ERP systems and internal NAS servers, ensuring 99.9\% uptime for business operations.}
        \resumeItem{Configured enterprise networking equipment and resolved complex workstation issues.}
      \resumeItemListEnd

    \resumeSubheading
      {Yuri Technology Co., Ltd.}{Mar 2025 -- Sep 2025}
      {Production Operator}{Tainan, Taiwan}
      \resumeItemListStart
        \resumeItem{Managed semiconductor packaging workflows and strictly adhered to safety/SOP standards.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming}{: C, C++, Python, Shell Scripting} \\
     \textbf{Mathematical Tools}{: Numerical Analysis, FDM, FEM, Probability, Statistics} \\
     \textbf{Systems \& Web}{: Linux (Ubuntu/CentOS), Server Administration, Networking, HTML} \\
     \textbf{Certifications}{: ISO/IEC 27001 ISMS Training}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}